MSc Statistical overview

### 2018-01-27 MScFigures.Rmd
Added missing libraries

  * File creation date: `r Sys.Date()`
  * `r R.version.string`
  * `tidyverse` package version: `r packageVersion("tidyverse")`
  * `lme4` package version `r packageVersion("lme4")`
  * `MASS` package version `r packageVersion("MASS")`
  * `MuMIn` package version `r packageVersion("MuMIn")`
  * `emmeans` package version `r packageVersion("emmeans")`
  * `boot` package version `r packageVersion("boot")`
  * `brms` package version `r packageVersion("brms")`
  * `loo` package version `r packageVersion("loo")`
  * `fitdistrplus` package version `r packageVersion("fitdistrplus")`

@@

```{r Load_packages and functions, message=FALSE, warning=FALSE}
library(tidyverse)
library(lme4)
library(MASS)
library(MuMIn)
library(emmeans)
library(boot)
library(brms)
library(loo)
library(fitdistrplus)

>>>>

  * File creation date: `r Sys.Date()`
  * `r R.version.string`
  * `tidyverse` package version: `r packageVersion("tidyverse")`
  * `lme4` package version `r packageVersion("lme4")`
  * `MASS` package version `r packageVersion("MASS")`
  * `MuMIn` package version `r packageVersion("MuMIn")`
  * `emmeans` package version `r packageVersion("emmeans")`
  * `boot` package version `r packageVersion("boot")`
  * `brms` package version `r packageVersion("brms")`
  * `loo` package version `r packageVersion("loo")`
  * `fitdistrplus` package version `r packageVersion("fitdistrplus")`
  * `mefa` package version `r packageVersion("mefa")`
  * `library(devtools)` and `install_github("vqv/ggbiplot")` package version `r packageVersion("ggbiplot")`
  * also requires [rtools](https://cran.r-project.org/bin/windows/Rtools/)

@@

```{r Load_packages and functions, message=FALSE, warning=FALSE}
library(tidyverse)
library(lme4)
library(MASS)
library(MuMIn)
library(emmeans)
library(boot)
library(brms)
library(loo)
library(fitdistrplus)
library(mefa)
library(ggbiplot)
